Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-09 manuscript.Rmd
add links to prereg and its changes closes #213

The interested reader can find the example rendered as a pdf file with actual data in the [online supplementary material](this link does not work) and can view the changes we made since preregistering it on this [GitHub page](this link does not work).

>>>>

The interested reader can find the example rendered as a pdf file with actual data in the [online supplementary material](https://github.com/aaronpeikert/repro-tutorial/releases/tag/v0.0.2.0-results) and can view the changes we made since preregistering it on this [GitHub page](https://github.com/aaronpeikert/repro-tutorial/releases/tag/compav0.0.2.0-results).
